Exp-1 Met Results

### 2021-03-11 C.analysis/exp-1_met.Rmd
Materials and code for the March VCU meeting

library(ggplot2)
library(data.table)
library(fortedata)
library(magrittr)
library(fortedata)
library(ggpmisc)
library(assertthat)
library(GGally)
library(knitr)

@@

```{r}
# dt$`Disturbance Severity` <- paste0(dt$severity, ' %')
# 
# 
# lapply(unique(dt$label), function(l){
#   
#   dt[year >= 2015, ] %>% 
#   .[label == l, ] %>% 
#    ggplot(aes(year, value, color = `Disturbance Severity`, linetype = met)) + geom_vline(xintercept = 2019, color = 'black') + 
#   geom_line() + 
#    facet_wrap("scn") + 
#   THEME + 
#   theme(  strip.background = element_blank(),
#   strip.text.x = element_blank()) +
#   labs(y = 'Disturbance - Baseline', 
#        x = 'Year') + 
#   #, 
#   #     caption = 'vertical line 2019 disturbance event')  + 
#   scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
#   guides(linetype = FALSE) + 
#   labs(title = l)
#   
# }) -> 
#   plots
# names(plots) <- unique(dt$label)
# 
# 
# out <- plots$`Annual  Net primary productivity (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_NPP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual  Net Ecosystem productivity (kg/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_NEP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual  Gross primary productivity (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_GPP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual Mean Above-ground biomass (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_AGB.png"), 
#        height = 5,width = 8.5)

@@

@@

lapply(metric, function(m){
  #  & met_variable %in% c("prate", "tmp", "sh")
  full_df[metric_name == m] %>% 
  ggplot(aes(met_vavlue, metric_value, color = `Disturbance Severity`)) + 
  geom_point() + 
  facet_grid(variable ~ description, scales = "free",  labeller = label_wrap_gen(width = 20, multi_line = TRUE)) + 
  THEME + 
  labs(y = NULL, x = NULL, title = m) + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS)
}) -> 
  plots
names(plots) <- metric
```

@@

 ggsave(resistance_inputs, filename = file.path(FIG_OUT, "resistance_inputs.png"), width = 20, height = 10)
 resistance_inputs
```

>>>>

library(ggplot2)
library(data.table)
library(fortedata)
library(magrittr)
library(fortedata)
library(ggpmisc)
library(assertthat)
library(GGally)
library(knitr)
library(kableExtra)

@@

Create a summary table of the disturbance, the inital response to the disturbance

annual_data[year %in% c(2018, 2019), ] %>% 
  .[scn != "harvest_0_1day_above"] %>%  
  .[, .(scn, year, variable, value, met)] %>% 
  dcast(scn + variable + met ~ year) %>%  
  .[ , percent_change := 100 * (`2019` - `2018`) / `2018`] %>% 
  # summary stats!! 
  .[ , .(min = min(percent_change), 
         max = max(percent_change),
         mean = mean(percent_change), 
         sd = sd(percent_change)), by = .(scn, variable)] %>%  
  .[ , .(variable, scn, min, max, mean, sd)] -> 
summary_data

summary_data$variable <- gsub(pattern = "_patch",
                              replacement  = "",
                              x = summary_data$variable)
summary_data$severity <- gsub(pattern = "harvest_|_1day_above",
                              replacement = "", 
                              x = summary_data$scn)
summary_data[ , .(variable, severity, min, max, mean, sd)] %>%  
  setorder(variable) %>% 
  knitr::kable(format = "html", digits = 2) %>% 
  collapse_rows(columns = 1, valign = "top")

```{r}
annual_data[variable == "GPP_patch", ] %>% 
  .[year %in% c(2018:2021), ] %>% 
  ggplot(aes(year, value, color = scn)) + 
  geom_point()

```{r}
# Plot the individual disturbance severities

# dt$`Disturbance Severity` <- paste0(dt$severity, ' %')
# 
# 
# lapply(unique(dt$label), function(l){
#   
#   dt[year >= 2015, ] %>% 
#   .[label == l, ] %>% 
#    ggplot(aes(year, value, color = `Disturbance Severity`, linetype = met)) + geom_vline(xintercept = 2019, color = 'black') + 
#   geom_line() + 
#    facet_wrap("scn") + 
#   THEME + 
#   theme(  strip.background = element_blank(),
#   strip.text.x = element_blank()) +
#   labs(y = 'Disturbance - Baseline', 
#        x = 'Year') + 
#   #, 
#   #     caption = 'vertical line 2019 disturbance event')  + 
#   scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
#   guides(linetype = FALSE) + 
#   labs(title = l)
#   
# }) -> 
#   plots
# names(plots) <- unique(dt$label)
# 
# 
# out <- plots$`Annual  Net primary productivity (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_NPP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual  Net Ecosystem productivity (kg/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_NEP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual  Gross primary productivity (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_GPP.png"), 
#        height = 5,width = 8.5)
# 
# out <- plots$`Annual Mean Above-ground biomass (kgC/m2)`
# ggsave(out, filename = file.path(FIG_OUT, "disturbance_AGB.png"), 
#        height = 5,width = 8.5)

@@

  ggsave(recovery_at, filename = file.path(FIG_OUT, "recovery_at.png"), 
        height = 5,width = 8.5)
 recovery_at

@@

lapply(metric, function(m){
#    & met_variable %in% c("prate", "tmp", "sh")
  full_df[metric_name == m] %>% 
    .[met_variable %in%c("prate", "tmp", "sh")]%>% 
  ggplot(aes(met_vavlue, metric_value, color = `Disturbance Severity`)) + 
  geom_point() + 
  facet_grid(variable ~ description, scales = "free",  labeller = label_wrap_gen(width = 20, multi_line = TRUE)) + 
  THEME + 
  labs(y = NULL, x = NULL, title = m) + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS)
}) -> 
  plots
names(plots) <- metric
```

@@

 ggsave(resistance_inputs, filename = file.path(FIG_OUT, "resistance_inputs.png"), width = 5, height = 5)
 resistance_inputs
```
